Forecast of the 2024 Presidential Election through the Lens of Turbulent Battleground States

### 2024-11-04 paper/paper.qmd

# Model
In this analysis, we utilize a logistic regression model to predict polling percentages for the 2024 U.S. presidential candidates over time. In order to focus on states with historical significance in elections. The model is specified as a Generalized Linear Model (GLM) with a binomial family and a logit link function, appropriate for modeling binary or proportion-based outcomes.  The United State's electoral college system operates under a winner takes all votes mechanic where all the electoral votes are allocated to whichever candidate receives the larger share of votes within that state. Therefore, our model considers states outside the realm of swing states to have allocated a certain number of electoral votes to each candidate wherein Donald Trump has 219 seats and Kamala Harrris has  226. This initial distribution of electoral votes is provided by New York Times' tracking of swing states [@boyce_swing_states]. Our model will produce projected shares in each state from which the electoral votes of swing states will be allocated to each  candidate to predict the winner of the presidential election.

@@

# Discussion
## Turbulent Margins
Based on our results from @fig-1 predicted that Kamala Harris to win the presidential election with 276 electoral votes. Furthermore, @fig-2 showed that her lead in the states of Pennsylvania, Wisconsin, Nevada, and Michigan are stronger than Donald Trump's support in Pennsylvania, Wisconsin, Nevada, and Michigan. From @fig-2, we can also observe that Kamala Harris' lead in Nevada seems to be the weakest. In the framework of the electoral college system, losing Nevada to Donald Trump would not change the results as Nevada holds 6 electoral votes, which means that Kamala Harris would still possess the necessary 270 to win the election. However, this is not the case if Kamala Harris loses support in any of the three other states of Pennsylvania, Wisconsin, and Michigan as this would place her beneath the 270 seat threshold. In fact, losing any one of these states would result in Donald Trump's victory. @fig-3 showed that the support rate of Donald Trump is increasing faster than that of Kamala Harris', threatening Harris' lead over Pennsylvania, Wisconsin, and Michigan.

@@

# Appendix A {-}

#  Sampling Methodology Employed by New York Times and Siena College:

@@

# Sampling Approach: Stratified Sampling

@@

# Appendix B {-}

>>>>

# Model {#sec-model}
In this analysis, we utilize a logistic regression model to predict polling percentages for the 2024 U.S. presidential candidates over time. In order to focus on states with historical significance in elections. The model is specified as a Generalized Linear Model (GLM) with a binomial family and a logit link function, appropriate for modeling binary or proportion-based outcomes.  The United State's electoral college system operates under a winner takes all votes mechanic where all the electoral votes are allocated to whichever candidate receives the larger share of votes within that state. Therefore, our model considers states outside the realm of swing states to have allocated a certain number of electoral votes to each candidate wherein Donald Trump has 219 seats and Kamala Harrris has  226. This initial distribution of electoral votes is provided by New York Times' tracking of swing states [@boyce_swing_states]. Our model will produce projected shares in each state from which the electoral votes of swing states will be allocated to each  candidate to predict the winner of the presidential election.

@@

# Discussion {#sec-discussion}
## Turbulent Margins
Based on our results from @fig-1 predicted that Kamala Harris to win the presidential election with 276 electoral votes. Furthermore, @fig-2 showed that her lead in the states of Pennsylvania, Wisconsin, Nevada, and Michigan are stronger than Donald Trump's support in Pennsylvania, Wisconsin, Nevada, and Michigan. From @fig-2, we can also observe that Kamala Harris' lead in Nevada seems to be the weakest. In the framework of the electoral college system, losing Nevada to Donald Trump would not change the results as Nevada holds 6 electoral votes, which means that Kamala Harris would still possess the necessary 270 to win the election. However, this is not the case if Kamala Harris loses support in any of the three other states of Pennsylvania, Wisconsin, and Michigan as this would place her beneath the 270 seat threshold. In fact, losing any one of these states would result in Donald Trump's victory. @fig-3 showed that the support rate of Donald Trump is increasing faster than that of Kamala Harris', threatening Harris' lead over Pennsylvania, Wisconsin, and Michigan.

@@

# Appendix {-}

# Sampling Methodology Employed by New York Times and Siena College {#sec-Methodology}

@@

# Sampling Approach: Stratified Sampling {#sec-stratified-sampling}

@@

# Additional data details {#sec-additional_data_details}
